---
title: "data_cleaning"
author: "Rahul Hosalli"
date: "2022-09-20"
output: html_document
---

# Data Cleaning I

Load required packages

```{r}
library(tidyverse)
```

## Data Import

Data comes in a variety of formats (.csv, Excel, SAS, etc.) and there are a number of packages that ease loading data in R.

### CSVs

Loading CSV datasets are accomplished via the `read_csv` function (part of the `readr` package) which is an updated version of the base R CSV import function.

#### Important Sidebar

Make sure to use relative paths instead of absolute paths to increase the robustness of your code

    "./data/FAS_litters.csv"

```{r}
litters_df <- read_csv("./data/FAS_litters.csv")

# the janitor package will convert all column names to snake_case

litters_df <- janitor::clean_names(litters_df)
```

The `skimr::skim()` function provides summary statistics of your columns

```{r}
skimr::skim(litters_df)
```

#### Learning Assessment

```{r}
pups_df <- read_csv("./data/FAS_pups.csv")
```

## Looking at Data

The first step is to look at the data

```{r}
litters_df
tail(litters_df, 5)
```

`View` and `view` are both useful, but don't work particularly well in an RMarkdown. Run it from the console instead.
